\documentclass{letter}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\signature{Ilya Eryzhenskiy}
\address{Ilya Eryzhenskiy \\ CIRED: 45bis Av. de la Belle Gabrielle \\ Nogent-sur-Marne \\ 94130 France \\ +33758515488 \\ ilya.eryzh@gmail.com\\}
\begin{document}
\begin{letter}{Finance Department \\ 
Maastricht University \\
Minderbroedersberg 4-6 \\
6211 LK Maastricht\\
Netherlands \\
  ~ \\ \textbf{Subject: Application for the Assistant Professor  in Finance Position.}}
\opening{Dear Madam, Sir,}

I am delighted to apply for the position of Assistant Professor in Finance. As a postdoctoral researcher specialized in household finance, I find this position a perfect job opportunity. 

I believe that my focus on household finance complements the research agenda of the group in several directions. First, my work on the financing of energy efficient renovations contributes to the group's research strand on sustainable finance. Second, my current work on the pricing of sea level rise risk in mortgage loans will complement the climate risks \& real estate research agenda. Finally, my theoretical analysis on redistribution under financial frictions involves a life-cycle analysis of decisions around the retirement age, in line with the pension research agenda of the group.       

International work environments are an integral part of my life as a researcher. I am fluent in English, French and Russian, and have an intermediate level of German. My doctoral studies were done within the Erasmus Mundus Doctorate in Economics, with a one-year stay in Germany and annual meetings in various universities of the program. I then joined the International Center for Studies in Environment and Development for my post-doctoral studies. Having a taste for presenting my work in conferences and seminars, I have given talks in 7 countries since the beginning of my doctoral studies. 

% The \ldots command produces dots in a way that will not upset
% the typesetting of the document.

I have a rich teaching experience with a variety of methods. In total, I have taught 2 courses as a lecturer, 5 courses as a TA. Roughly one half of these courses has been taught in English, the other has been taught in French. Supervision of student projects has been a particular interest of mine, at both Bachelor and Master level.

That said, I would like to express my enthusiasm with respect to this Assistant Professor position, which is a great fit for my skills -- both soft and hard ones.  
Thank you for your time and consideration.

I look forward to our future exchanges. \\
~ \\
    
{Yours faithfully, \\
~ \\
Ilya Eryzhenskiy}

\end{letter}
\end{document}
