\documentclass{letter}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\signature{Ilya Eryzhenskiy}
\address{Ilya Eryzhenskiy \\ CIRED: 45bis Av. de la Belle Gabrielle \\ Nogent-sur-Marne \\ 94130 France \\ +33758515488 \\ ilya.eryzh@gmail.com\\}
\begin{document}
\begin{letter}{THEMA (Theorie Economique, Modelisation et Applications), CY Cergy Paris Université \\ To whom it may concern \\Pontoise FR, 33 Bd du Port \\Cergy\\95000 France\\
  ~ \\ \textbf{Subject: Application for the Assistant Professor Position.}}
\opening{Dear Madam, Sir,}

I am writing to you to apply for the Assistant Professor (tenure track) position that is advertised on the Econjobmarket portal. As a postdoctoral researcher in household finance and green finance, I find this position a perfect job opportunity. 

I believe I am a fitting candidate for the Assistant Professor position at the University for the following reasons. First, I have sharp analytical skills that allow me to analyze both empirical data and theoretical models, as exposed in my job market paper and the second paper attached to my application. My research is at an intersection of finance and other relevant fields, such as macroeconomics and environment economics. Second, I have successfully combined research with teaching, in both English and French, in the past 7 years. I speak English, French and Russian fluently and have an intermediate level of German. Finally, I have some experience in the business environment from an internship in a finance department of an international company. 

% The \ldots command produces dots in a way that will not upset
% the typesetting of the document.
I will contribute to the banking and real estate axes of the Department's research. Namely, I am currently working on such topics as loans for housing renovation, consumer credit and the macroeconomy, asset bubbles, and the impact of climate change on housing credit. 

That said, I would like to express my enthusiasm with respect to this position, where I can make use of my analytical skills for research in a stimulating environment.  
Thank you for your time and consideration.

I look forward to our future exchanges.
\begin{flushright}
\closing{Yours Faithfully,}
\end{flushright}

\end{letter}
\end{document}
